\documentclass[10pt, french]{article}
%% -----------------------------
%% Préambule
%% -----------------------------
\input{../preambule.tex}
%% -----------------------------
%% Redefine from template
%% -----------------------------
\def\auteur{Alec James van Rassel}
%% -----------------------------
%% Variable definition
%% -----------------------------
\def\cours{Secrets of mental math}
%\def\sigle{Arthur Ben}
\usepackage[landscape, hmargin=1cm, vmargin=1.7cm]{geometry}
\usepackage{multicol}

%% -----------------------------
%% Colour setup for sections
%% -----------------------------
\def\SectionColor{burntorange}
\def\SubSectionColor{burntsienna}
\def\SubSubSection{burntsienna}

% 
% Débute numérotation des chapitres à 2 pour suivre les notes de Marie-Piere.
% 
\setcounter{section}{1}

%% -----------------------------
%% Début du document
%% -----------------------------
\begin{document}

\begin{multicols*}{3} 
\section*{Quick tricks}
\begin{CHPT_SUMM}{Multiplication by 11}
We insert the sum between the 2 original numbers.
For example:
	\begin{align*}
		33 \times 11	
		&=	3 \textcolor{cyan}{6}3
	\end{align*}
If the sum is more than 9, we simply carry over. 
For example:
	\begin{align*}
		93 \times 11	
		&=	\textcolor{teal}{10} \textcolor{cyan}{2} 3
	\end{align*}
where we had $9 + 3 = 12$.
If we want to multiply larger numbers, the same rule carries over.
For example:
	\begin{align*}
		427 \times 11
		&=	4 \textcolor{teal}{6} \textcolor{cyan}{9}7
	\end{align*}
where we had $\textcolor{teal}{4 + 2 = 6}$ and $\textcolor{cyan}{2 + 7 = 9}$.
\end{CHPT_SUMM}

\begin{CHPT_SUMM}{Multiplying 2 numbers whose first digit is the same and whose second sums to 10}
The procedure is to multiply the first digit by the next number and to multiply the second digits together.
For example :
	\begin{align*}
	35 \times 35
	&=	\textcolor{teal}{12}\textcolor{cyan}{25}
	\end{align*}
with $\textcolor{teal}{3 \times 4 = 12}$ and $\textcolor{teal}{5 \times 5 = 25}$.

It is important to have 2 digits for the multiplication of the second digit. 
For example:
	\begin{align*}
	31 \times 39
	&=	\textcolor{teal}{12}\textcolor{cyan}{09}
	\end{align*}
with $\textcolor{teal}{3 \times 4 = 12}$ and $\textcolor{teal}{1 \times 9 = 09}$.
\end{CHPT_SUMM}

\begin{CHPT_SUMM}{Squaring any number}
The algebraic formula is, where $A$ and $d$ are integers, $A^{2} = (A + d) \times (A - d) + d^{2}$.
For example:
	\begin{align*}
	98^{2}	
	&=	100 \times 96 + 2^{2}
	=	960\textcolor{teal}{4}
	\end{align*}
with the number $\textcolor{teal}{2}$ being added and substracted and from $98$.

We can generalize this to 3 digit numbers.
For example:
	\begin{align*}
	212^{2}	
	&=	2\textcolor{teal}{00} \times 224 + 12^{2}	\\
	&=	448\textcolor{teal}{00} + 144
	=	44944
	\end{align*}
	
Because we round down to the nearest hundred, we only have to multiply the first digit.
\end{CHPT_SUMM}

\begin{CHPT_SUMM}{Multiplying numbers between 10 and 20}
We add the second digit of the second number to the first and add the multiple of the second digit for both numbers.
For example:
	\begin{align*}
	17 \times 14
	&=	\textcolor{cyan}{(17 + 4)} \times \textcolor{amethyst}{10} + \textcolor{teal}{7 \times 4}	\\
	&=	\textcolor{cyan}{21}\textcolor{amethyst}{0} + \textcolor{teal}{28}	
	=	238
	\end{align*}
\end{CHPT_SUMM}


\begin{CHPT_SUMM}{Almost perfect squares}
Recall that \icbox{$x^{2}	-	1	=	(x	-	1)(x		+	1)$}. In fact, $x^{2}$ can be visualized as a square from which we substract one to form a rectangle of lengths $x	-	1$ and $x	+	1$.
\end{CHPT_SUMM}

\pagebreak
\section{Dates and units}
Since 1582 (introduction of the Gregorian calendar).\\

A year is a leap year if :
\begin{itemize}
	\item	The year can be divided by 4 (e.g., 2016, 2020, 2024, etc.).
	\item	The year cannot be divided by 100 (e.g., 2100, 2200, etc.).
	\item	Except if it can be divided by 400 (e.g., 2000, 2400, etc.).	
\end{itemize}

\subsection{Find day of the week of any date}
We pose : 
\begin{description}
	\item[$h$]	Day of the week with $\{0 = \text{Sat.}, 1 = \text{Sun.}, 2 = \text{Mon.}, \dots, 6 = \text{Fri.}\}$.
	\item[$d_{m}$]	Day of the month.
	\item[$m$]	Month with $\{3 = \text{Mar.}, 4 = \text{Apr.}, 2 = \text{Mon.}, \dots, 14 = \text{Feb.}\}$.
		\begin{itemize}
		\item	So we'd consider February to be the 14th month of the previous year.
		\end{itemize}
	\item[$K$]	Year of the century, $Y mod 100$.
	\item[$J$]	Zero-based century, $\lfloor Y / 100\rfloor$.
\end{description}

So, $h	=	\left(d_{m} + \lfloor \frac{13(m + 1)}{4} \rfloor + K + \lfloor \frac{K}{4} \rfloor +  + \lfloor \frac{J}{4} \rfloor - 2J\right) mod 7$.

\subsection{Temperature}
\begin{description}
	\item[$\deg C$ to $\deg F$]	Multiply by 9, divide by 5 and add 32.
	\item[$\deg F$ to $\deg C$]	Deduct 32, multiply by 5 and divide by 9.
\end{description}
Alternatively, we can multiply \textit{(divide)} by 1.8 (i.e.,  9/5) to convert from $\deg C$ to $\deg F$ \textit{(or vice-versa)}.

\end{multicols*}
%% -----------------------------
%% Fin du document
%% -----------------------------
\end{document}
